### 2015-05-14 Draft/abstract.tex
Updated Brittnay's feedback

Temporal constraints of an Application Programming Interface (API)
are the allowed sequences of method invocations in the API.
These constraints govern the secure and robust operation of client software using the API.
However, in practice, most APIs do not come with formal temporal constraints.
In contrast, these constraints are typically described
informally in natural language API documents, and therefore are not amenable
to existing tools for checking formal temporal constraints.
\textit{The goal of this work is to assist developers to construct API clients that comply with 
temporal constraints of the API through the inference and formalization of these constraints found in natural language API documents.}
Since API documents are often verbose, manually identifying and writing formal temporal constraints can be prohibitively time-consuming and error-prone.
To address this issue,
we propose \tool: an approach based on Machine Learning (ML) and Natural Language Processing (NLP) for identifying and inferring formal temporal constraints.
To evaluate our approach, we apply \tool\ to infer and formalize temporal
constraints from the \amazonAPI, the \paypalAPI\, and the \CodeIn{java.io} package in the
JDK API.
Our results indicate that \tool\ is effective in identifying temporal
constraint sentences (from over
4000 human-annotated API sentences) with the average precision, recall, and F-score
of 79.0\%, 60.0\%, and 65.0\%, respectively.
Furthermore, our evaluation also demonstrates that \tool\ achieves an accuracy of 70\% in inferring and formalizing 77 temporal constraints from these temporal constraint sentences.

>>>>

Temporal constraints of an Application Programming Interface (API)
are the allowed sequences of method invocations in the API.
These constraints govern the secure and robust operation of client software using the API.
However, in practice, most APIs do not come with formal temporal constraints.
In contrast, these constraints are typically described
informally in natural language API documents, and therefore are not amenable
to existing tools for checking formal temporal constraints.
\textit{The goal of this work is to assist developers to construct API clients that comply with 
temporal constraints of the API through the inference and formalization of these constraints found in natural language API documents.}
Since API documents are often verbose, manually identifying and writing formal temporal constraints can be prohibitively time-consuming and error-prone.
To address this issue,
we propose \tool: an approach based on Machine Learning (ML) and Natural Language Processing (NLP) for identifying and inferring formal temporal constraints.
To evaluate our approach, we use \tool\ to infer and formalize temporal
constraints from the \amazonAPI, the \paypalAPI\, and the \CodeIn{java.io} package in the
JDK API.
Our results indicate that \tool\ can effectively identify temporal
constraint sentences (from over
4000 human-annotated API sentences) with the average precision, recall, and F-score
of 79.0\%, 60.0\%, and 65.0\%, respectively.
Furthermore, our evaluation also demonstrates that \tool\ achieves an accuracy of 70\% in inferring and formalizing 77 temporal constraints from these temporal constraint sentences.

### 2015-05-14 Draft/approach.tex
Updated Brittnay's feedback

We next present our approach for inferring temporal constraints
from the method descriptions in API Documents.
Figure~\ref{fig:approachOverview} gives an overview of the \tool\ approach.
\tool\ consists of following six major components: a preprocessor, a candidate identifier, a text-analysis engine, a semantic graph generator, constraint extractor, and a type analyzer.
Additionally, there is an optional model trainer component and external NLP parser component.

@@

This component accepts the annotated sentence from the previous component,
then using a trained ML model classifies whether a sentence describes a temporal constraint or not. We next describe the model construction.

@@

3) \textbf{Lemmatization}: The feature is the base form of a word. In linguistic, lemmatization is the reduction of operational form of a word to its base form. For instance, ``invoking'', ``invokes'', and ``invoked'' are all reduced to invoke. The rationale for reducing the words to base form is to reduce the size of the feature set that otherwise considers every word form as an independent feature.

@@

5) \textbf{Stanford Dependencies}: We add to the feature set by identifying the presence of specific Stanford typed dependencies pertaining to the temporal aspects of the sentence semantics. In particular, we identify the presence of ``\textit{advcl}'', ``\textit{aux}'', ``\textit{auxpass}'', ``\textit{vmod}'', and ``\textit{tmod}''. For instance, the annotated sentence in Figure~\ref{fig:standep} contains both ``\textit{aux}'' and ``\textit{auxpass}'' dependencies. These are both added to the feature set.

@@

Constraint Extractor is responsible for inferring temporal constraint from the classified constraint sentences. Temporal constraints are expressed as temporal formulae involving: a) \textit{Predicates} $\xi$ representing method calls and b) \textit{Temporal operators}: backward ($\leftarrow$) \& forward ($\rightarrow$) and their negations $\xleftarrow{-}$ \& $\xrightarrow{-}$. We define following four constraints:

@@

\textbf{$\xi_1$}:
\tool\ first identifies $\xi_1$ as the method whose description constraint sentence is part of.
For instance the sentence in Figure~\ref{fig:standep} is part of Delete Bucket method description in \amazonAPI,
$\xi_1$ is instantiated as Delete Bucket method.

\textbf{$\xi_2$}:
\tool\ next identifies $\xi_2$. Since, references to $\xi_2$ may not always be implicit we leverage the semantic graphs. A semantic graph is a representation of concepts of objects and the methods applicable on those objects. Figure~\ref{fig:knowledge} shows a graph for \CodeIn{Object} resource in \amazonAPI.
The phrases in rounded rectangle are the actions applicable on \CodeIn{Object} resource.
Section~\ref{sub:ACA} further describes how these graphs are generated.
%\tool\ uses the Algorithm~\ref{alg:SenAnnotaator} to identify $\xi_2$.

@@

The negation is identified by presence of negation verbs such as ``\textit{no}'', ``\textit{not}'', ``\textit{can't}'' ... etc. Another rule for negation operator is if the sentence is in exception/error description.

@@

\subsection{Type Analysis}

Some temporal constraints are enforced by the type system in typed Languages.
For instances a method ($m$) accepting input parameter ($i$) of type ($t$) mandates that (at least one) method ($m'$) be invoked whose return value is of type ($t$).
To extend the temporal constraints inferred by the analyzing the natural language text, this component infers additional constraints that are encoded
in the type system. %Algorithm~\ref{alg:TypeAnalysis} lists the steps followed to infer type based temporal constraints.

>>>>

We next present our approach for inferring temporal constraints
from the method descriptions in API Documents.
Figure~\ref{fig:approachOverview} gives an overview of the \tool\ approach.
\tool\ consists of six major components: a preprocessor, a candidate identifier, a text-analysis engine, a semantic graph generator, constraint extractor, and a type analyzer.
Additionally, there is an optional model trainer component and external NLP parser component.

@@

This component accepts the annotated sentence from the previous component,
then using a trained ML model classifies whether each sentence as a temporal constraint sentence or not. We next describe the model construction.

@@

3) \textbf{Lemmatization}: The features are the lemma of a words occurring in the sentences. In linguistic, lemmatization is the reduction of operational form of a word to its base form. For instance, ``invoking'', ``invokes'', and ``invoked'' are all reduced to invoke. The rationale for reducing the words to base form is to reduce the size of the feature set that otherwise considers every word form as an independent feature.

@@

5) \textbf{Stanford Dependencies}: We add to the feature set by identifying the presence of specific Stanford-typed dependencies pertaining to the temporal aspects of the sentence semantics. In particular, we identify the presence of ``\textit{advcl}'', ``\textit{aux}'', ``\textit{auxpass}'', ``\textit{vmod}'', and ``\textit{tmod}''. For instance, the annotated sentence in Figure~\ref{fig:standep} contains both ``\textit{aux}'' and ``\textit{auxpass}'' dependencies. These are both added to the feature set.

@@

Constraint Extractor is responsible for inferring temporal constraint from the classified constraint sentences.
Temporal constraints are expressed as temporal formulae involving: 
a) \textit{Predicates} $\xi$ representing method calls and 
b) \textit{Temporal operators}: backward ($\leftarrow$) \& forward ($\rightarrow$) and their negations $\xleftarrow{-}$ \& $\xrightarrow{-}$.
We define the following four constraints:

@@

\textbf{$\xi_1$}:
\tool\ first identifies $\xi_1$ as the method whose description the constraint sentence is part of.
For instance the sentence in Figure~\ref{fig:standep} is part of Delete Bucket method description in \amazonAPI,
$\xi_1$ is instantiated as Delete Bucket method.

\textbf{$\xi_2$}:
\tool\ next identifies $\xi_2$. Since, references to $\xi_2$ may not always be implicit we leverage the semantic graphs. 
A semantic graph is a representation of objects and the methods applicable on those objects.
Figure~\ref{fig:knowledge} shows a graph for \CodeIn{Object} resource in \amazonAPI.
The phrases in rounded rectangle are the actions applicable on \CodeIn{Object} resource.
Section~\ref{sub:ACA} further describes how these graphs are generated.
%\tool\ uses the Algorithm~\ref{alg:SenAnnotaator} to identify $\xi_2$.

@@

The negation is identified by presence of the negation verbs such as ``\textit{no}'', ``\textit{not}'', ``\textit{can't}'' ... etc.
Another rule for negation operator is if the sentence is in exception/error description.

@@

\subsection{Type Analysis}
\label{sub:typeAnalysis}

Some temporal constraints are enforced by the type system in typed Languages.
For instance, a method ($m$) accepting input parameter ($i$) of type ($t$) mandates that (at least one) method ($m'$) be invoked whose return value is of type ($t$).
To extend the temporal constraints inferred by the analyzing the natural language text, this component infers additional constraints that are encoded
in the type system. %Algorithm~\ref{alg:TypeAnalysis} lists the steps followed to infer type based temporal constraints.

### 2015-05-14 Draft/background.tex
Updated Brittnay's feedback

We next briefly introduce the techniques used in this work that have been grouped into two broad categories.
We first introduce the core NLP techniques used in this work.
We then introduce the SE specific NLP techniques proposed in related work~\cite{pandita12:inferring,pandita13:WHYPER} that are leveraged in this work.

@@

{\small $\bullet$} \textbf{Typed Dependencies}~\cite{Marneffe06LREC,Marneffe08COLING}: The Stanford typed dependencies representation  is designed to provide a simple description of grammatical relationships directed towards non-linguistics experts to perform NLP related tasks. The representation provides a hierarchical structure for the dependencies with precise definitions of what each dependency represents, thus facilitating machine based manipulation of natural language text.

>>>>

We next briefly introduce the NLP techniques used in this work that have been grouped into two broad categories.
We first introduce the core NLP techniques.
We then introduce the SE specific NLP techniques proposed in related work~\cite{pandita12:inferring,pandita13:WHYPER}.

@@

{\small $\bullet$} \textbf{Typed Dependencies}~\cite{Marneffe06LREC,Marneffe08COLING}: The Stanford typed dependencies representation is designed to provide a simple description of grammatical relationships directed towards non-linguistics experts to perform NLP related tasks. The representation provides a hierarchical structure for the dependencies with precise definitions of what each dependency represents, thus facilitating machine-based manipulation of natural language text.

### 2015-05-14 Draft/evaluation.tex
Updated Brittnay's feedback

\subsection{Evaluation Setup} 
We first manually annotated the sentences in the API documents of the subject APIs.
The first two authors manually labeled each sentence (2417 total) in the Java API documentation as being a temporal constraint sentence or not.
We used \CodeIn{cohen kappa}~\cite{carletta1996assessing} score to statistically measure
the inter-rater agreement.
The \CodeIn{cohen kappa} score of the two authors was .66 (on a scale of 0 to 1), 
which denotes a statically significant agreement~\cite{carletta1996assessing}. 
After the authors classified all the sentences, they 
discussed with each other to reach a consensus on the sentences they classified differently.
We use these classified sentences as the golden set for evaluating effectiveness of \tool.
Table~\ref{tab:results} lists the subject statistics.
Based on the discussions with regards to annotation of \CodeIn{java.io} API, first author annotated the rest of the subject APIs.

@@

To answer RQ2, we manually verified the temporal constraints inferred from constraint sentences by \tool.
However, we excluded the type-enforced temporal constraints inferred using Algorithm~\ref{alg:TypeAnalysis}, described in Section~\ref{sec:approach}.
We excluded the type-enforced constraints because they are correct by construction and are by default enforced by modern IDE's such as the Eclipse. 
We then measure $accuracy$ of \tool\ as the ratio of the total number of temporal constraints that
are correctly inferred by \tool\ to the total number of constraint sentences. Two authors
independently verified the correctness of the temporal constraints inferred by \tool.
We define the \CodeIn{accuracy} of \tool\ as the ratio of constraint sentences with correctly inferred temporal constraints
to the total number of constraint sentences. 
Higher value of \CodeIn{accuracy} is indicative of effectiveness of \tool\ in inferring temporal constraints from constraint sentences.

To answer RQ3, we counted the overlap in the temporal constraints inferred by \tool\ 
from the natural language text in API documents to the type-enforced temporal constraints
inferred using Algorithm~\ref{alg:TypeAnalysis}, described in Section~\ref{sec:approach}.

@@

We next present our evaluation results.

@@

Our results show that, \tool\ effectively identifies constraint sentences with the average (across different classifiers) \CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-score} of 79.0\%, 60.0\%, and 65.0\%, respectively.
Balanced Winnow performed best, with an average \CodeIn{precision} and \CodeIn{recall} of 78\% and 77\% respectively. 
Furthermore, our results also show the features proposed by \tool\ improves the precision of classification algorithms by an average of 18\%. There is also a slight increase in the recall (average 1\% gain).

@@

In this section, we evaluate the effectiveness of \tool\ in inferring temporal constraints from the identified constraint sentences from API documents.Table~\ref{tab:results} shows the effectiveness of \tool\ in inferring temporal constraints from the identified constraint sentences.
Column ``API'' lists the names of the subject API. 
Columns ``Mtds'' and ``Sen'' list the number of methods and sentences in each subject API's.
Column ``Sen$_C$'' lists the number of manually identified constraint sentences.
Column ``Spec$_{ICON}$'' lists the number of sentences with correctly inferred temporal constraints by \tool. 
Column ``Acc(\%)'' list percentage values of accuracy. 
Our results show that, out of 90 manually identified constraint sentences, \tool\ correctly infers temporal constraints with the average accuracy of 70.0\%.

@@

We next present an example to illustrate how \tool\ fails infer constraints from a constraint sentence.
%False negatives are undesirable in the context of our problem domain
%because they can mislead the users of \tool\ into believing that no other temporal constraint exists in the API documents.
%Furthermore, an overwhelming number of false negatives works against the practicality of \tool.
For instance, consider the sentence ``\textit{This implementation of the PUT operation creates a copy of an object that is already stored in Amazon S3.}''
from  \CodeIn{PUT Object-Copy} method description in \amazonAPI.
The sentence describes the constraint that the object must already be stored (invocation of \CodeIn{PUT Object})
before calling the current method.
However, \tool cannot make the connection owing to the limitation of the semantic graphs that do not list ``already stored'' as a ``valid operation'' on object.  
In the future, we plan to investigate techniques to further improve knowledge graphs to infer such implicit constraints.

@@

To address this question, we manually inspect each of the constraints reported by ICON and classify it as a type-enforced constraint or a non type-enforced constraint. 
We observed that none of the constraints inferred by our \tool\ from natural language text were classified as a type-enforced constraint.
Hence, the constraints detected by \tool\ are not trivial enough to be enforced by a type system.

@@

In summary, we demonstrate that \tool\ effectively identifies constraint sentences (from over 4000 API sentences) with the average precision, recall, and F-score of 79.0\%, 60\%, and 65\% respectively. We also show that \tool\ infers temporal constraints from the constraint sentences an average accuracy of 70\%. Furthermore, also provide discussion on why \tool\ does not or incorrectly infers temporal constraints. Finally, we provide a comparison of the temporal constraints inferred from natural language description against the temporal constraints enforced by a type system.

>>>>

\subsection{Evaluation Setup} 
We first manually annotated the sentences in the API documents of the subject APIs.
The first two authors manually labeled each sentence (2417 total) in the Java API documentation as being a temporal constraint sentence or not.
We used cohen kappa~\cite{carletta1996assessing} score to statistically measure
the inter-rater agreement.
The \CodeIn{cohen kappa} score of the two authors was .66 (on a scale of 0 to 1), 
which denotes a statically significant agreement~\cite{carletta1996assessing}. 
After the authors classified all the sentences, they 
discussed with each other to reach a consensus on the sentences they classified differently.
We use these classified sentences as the golden set for evaluating effectiveness of \tool.
Table~\ref{tab:results} lists the subject statistics.
Based on the discussions with regards to annotation of \CodeIn{java.io} API, first author annotated the rest of the subject APIs.

@@

To answer RQ2, we manually verified the temporal constraints inferred from constraint sentences by \tool.
However, we excluded the type-enforced temporal constraints described in Section~\ref{sub:typeAnalysis}.
We excluded the type-enforced constraints because they are correct by construction and are by default enforced by modern IDE's such as the Eclipse. 
We then measure $accuracy$ of \tool\ as the ratio of the total number of temporal constraints that
are correctly inferred by \tool\ to the total number of constraint sentences. Two authors
independently verified the correctness of the temporal constraints inferred by \tool.
We define the \CodeIn{accuracy} of \tool\ as the ratio of constraint sentences with correctly inferred temporal constraints
to the total number of constraint sentences. 
Higher value of \CodeIn{accuracy} is indicative of effectiveness of \tool\ in inferring temporal constraints from constraint sentences.

To answer RQ3, we counted the overlap in the temporal constraints inferred by \tool\ 
from the natural language text in API documents to the type-enforced temporal constraints
inferred using the method in Section~\ref{sub:typeAnalysis}.We next present our evaluation results.

@@

@@

Our results show that \tool\ effectively identifies constraint sentences with the average (across different classifiers) \CodeIn{precision}, \CodeIn{recall}, and \CodeIn{F-score} of 79.0\%, 60.0\%, and 65.0\%, respectively.
Balanced Winnow performed best, with an average \CodeIn{precision} and \CodeIn{recall} of 78\% and 77\% respectively. 
Furthermore, our results also show the features proposed by \tool\ improves the precision of classification algorithms by an average of 18\%. There is also a slight increase in the recall (average 1\% gain).

@@

%In this section, we evaluate the effectiveness of \tool\ in inferring temporal constraints from the identified constraint sentences from API documents.
Table~\ref{tab:results} shows the effectiveness of \tool\ in inferring temporal constraints from the identified constraint sentences.
Column ``API'' lists the names of the subject API. 
Columns ``Mtds'' and ``Sen'' list the number of methods and sentences in each subject API's.
Column ``Sen$_C$'' lists the number of manually identified constraint sentences.
Column ``Spec$_{ICON}$'' lists the number of sentences with correctly inferred temporal constraints by \tool. 
Column ``Acc(\%)'' list percentage values of accuracy. 
Our results show that, out of 90 manually identified constraint sentences, \tool\ correctly infers temporal constraints with the average accuracy of 70.0\%.

@@

We next present an example to illustrate how \tool\ fails infer constraints from a constraint sentence.
%False negatives are undesirable in the context of our problem domain
%because they can mislead the users of \tool\ into believing that no other temporal constraint exists in the API documents.
%Furthermore, an overwhelming number of false negatives works against the practicality of \tool.
For instance, consider the sentence ``\textit{This implementation of the PUT operation creates a copy of an object that is already stored in Amazon S3.}''
from  \CodeIn{PUT Object-Copy} method description in \amazonAPI.
The sentence describes the constraint that the object must already be stored (invocation of \CodeIn{PUT Object})
before calling the current method.
However, \tool\ cannot make the connection due to the limitation of the semantic graphs that do not list ``already stored'' as a ``valid operation'' on object.  
In the future, we plan to investigate techniques to further improve knowledge graphs to infer such implicit constraints.

@@

To address this question, we manually inspected each of the constraints reported by ICON and classify it as a type-enforced constraint or a non type-enforced constraint. 
We observed that none of the constraints inferred by our \tool\ from natural language text were classified as a type-enforced constraint.
Hence, the constraints detected by \tool\ are not trivial enough to be enforced by a type system.

@@

In summary, we demonstrate that \tool\ effectively identifies constraint sentences (from over 4000 API sentences) with the average precision, recall, and F-score of 79.0\%, 60\%, and 65\% respectively [RQ1]. We also show that \tool\ infers temporal constraints from the constraint sentences an average accuracy of 70\% [RQ2]. Furthermore, also provide discussion on why \tool\ does not or incorrectly infers temporal constraints. Finally, we provide a comparison of the temporal constraints inferred from natural language description against the temporal constraints enforced by a type system [RQ3].

### 2015-05-14 Draft/introduction.tex
Minor gramatical edits
Updated Brittnay's feedback

Application Programming Interfaces (APIs) facilitate software reuse
by providing standardized mechanism to access API components.
However, an API has some constraints governing the proper use of the API that must be followed.
One such type of constraints are temporal constraints [2], which are the allowed sequences of invocations of methods from the API.
Non-compliance to such constraints will often result in faulty applications that are unreliable to use. % and may even result in financial losses.

Formal analysis tools, such as model checkers and runtime verifiers 
can assist in detecting violations of the temporal constraints
in API clients as defects~\cite{lee2012towards}.
These tools typically accept formal representation of the temporal constraints for detecting violations.
However, temporal constraints are typically described in natural language text of API documents.
Such documents are provided to client-code developers through an online access, or are shipped with the API code.
For a method under consideration, API document may describe both the constraints on the method parameters
as well as the temporal constraints in terms of other methods that must be invoked pre/post invoking that method.
%We observe that a non-trivial portion (roughly 12\%) of the sentences (constraint-describing sentences)
%in \amazonAPI\ documentation describe temporal constraints.

@@

The first step towards formalizing temporal constraints is to identify the sentences describing such constraints.
A naive approach to identify the constraint sentences is to perform keyword-based search on API documents.
However, the effectiveness of such approach is limited by the quality of the keywords used.
Furthermore, sentences involving temporal constraints often the time may not have uniquely identifiable keywords.

@@

An ML based approach for identifying the temporal constraint sentences addresses the limitations of keyword-based search by automatically learning patterns of temporal constraint sentences.
Furthermore, we propose to use a combination of words, syntax (parts of speech) of a sentence, and semantics (relationship between words) of a sentence as the features for learning patterns.
This combination allows \tool\ to make a finer grained distinction between the example sentences described earlier.
Furthermore, to identify the phrases as implicit method-invocation references, we propose to leverage domain dictionaries that are systematically created from API documents and generic English dictionaries.

@@

\begin{itemize}
	\item An ML and NLP-based approach that effectively infers formal temporal constraints of method invocations. 
	%To the best of our knowledge, our approach is the first one to apply NLP for inferring temporal constraints from API documents.
	\item A prototype implementation of our approach based on extending the Stanford Parser~\cite{Klein03}, which is a natural language parser to derive the grammatical structure of sentences.
	All our experimental subjects, results, and artifacts are publicly available on our project website\footnote{\url{https://sites.google.com/site/temporalspec}}. 
	\item An evaluation of our approach on the \amazonAPI, the \paypalAPI, and the commonly used package \CodeIn{java.io} from the JDK API. 
\end{itemize}

>>>>

Application Programming Interfaces (APIs) facilitate software reuse
by providing a standardized mechanism to access API components.
However, an API has some constraints governing the proper use of the API that must be followed.
One such type of constraints are temporal constraints [2], which are the allowed sequences of invocations of methods from the API.
Non-compliance to such constraints will often result in faulty applications that are unreliable. % and may even result in financial losses.

Formal analysis tools, such as model checkers and runtime verifiers, 
can assist in detecting violations of the temporal constraints
in API clients as defects~\cite{lee2012towards}.
These tools typically accept a formal representation of the temporal constraints for detecting violations.
However, temporal constraints are typically described in natural language text of API documents.
Such documents are provided to client-code developers through an online access, or are shipped with the API code.
For a method under consideration, an API document may describe both the constraints on the method parameters
as well as the temporal constraints in terms of other methods that must be invoked pre/post invoking that method.
%We observe that a non-trivial portion (roughly 12\%) of the sentences (constraint-describing sentences)
%in \amazonAPI\ documentation describe temporal constraints.

@@

The first step towards formalizing temporal constraints is to identify the sentences describing such constraints.
A naive approach to identify the constraint sentences is to perform keyword-based search on API documents.
However, the effectiveness of such an approach is limited by the quality of the keywords used.
Furthermore, sentences involving temporal constraints often the time may not have uniquely identifiable keywords.

@@

An ML-based approach for identifying the temporal constraint sentences addresses the limitations of keyword-based search by automatically learning patterns of temporal constraint sentences.
Furthermore, we propose to use a combination of words, syntax (parts of speech) of a sentence, and semantics (relationship between words) of a sentence as the features for learning patterns.
This combination allows \tool\ to make a finer grained distinction between the example sentences described earlier.
Furthermore, to identify the phrases as implicit method-invocation references, we propose to leverage domain dictionaries that are systematically created from API documents and generic English dictionaries.

@@

\begin{itemize}
	\item A ML- and NLP-based approach that effectively infers formal temporal constraints of method invocations. 
	%To the best of our knowledge, our approach is the first one to apply NLP for inferring temporal constraints from API documents.
	\item A prototype implementation of our approach based on extending the Stanford Parser~\cite{Klein03}, which is a natural language parser to derive the grammatical structure of sentences.
	All our experimental subjects, results, and artifacts are publicly available on our project website.~\footnote{\url{https://sites.google.com/site/temporalspec}} 
	\item An evaluation of our approach on the \amazonAPI, the \paypalAPI, and the commonly used package \CodeIn{java.io} from the JDK API. 
\end{itemize}
